### 2017-11-21 manuscript.rmd
fixed sex state for Rudjakovia, fixed rotation of tree with all siph species

#Load tree
tree = species_tree_unladder
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
#tree<-rotateNodes(tree,nodes=c(28,31))
tree<-rotateNodes(tree,nodes=ape::mrca(tree)["Agalma elegans","Hippopodius hippopus"])

ultratree <- chronos(tree)
class( ultratree ) = "phylo"

>>>>

#Load tree
tree = species_tree_unladder
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
#tree<-rotateNodes(tree,nodes=c(28,31))

ultratree <- chronos(tree)
class( ultratree ) = "phylo"
nodes_to_rotate = c(ape::mrca(ultratree)["Physalia physalis","Kephyes ovata"], ape::mrca(ultratree)["Bargmannia lata","Hippopodius hippopus"])
ultratree<-rotateNodes(ultratree,nodes=nodes_to_rotate)
